Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2012-03-07 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2012:03:07	14:59:18	(Wed 7.Mar)

@@

\IEEEPARstart{T}{o} form images from a modern phased array sonar system the received waveform is usually recorded, and then processed by a digital beamformer. Estimating one pixel at a time, the beamformer adjusts the arrays spatial response to ensure the maximum gain in the direction of the pixel of interest, while maintaining maximum suppression at all other angles.

@@

\begin{itemize}
\item Why beamforming?
\item Adaptive beamformers
\item Challenges in active sonar systems. Correlated noise, robustification kills the adaptive potential. Quite computationally intensive.
\item LCA is like DAS, only we test several windows and choose the one that yield the lowest beamformer output power. Ultrasound \cite{Synnevag2008}, active sonar \cite{Buskenes2011}\cite{Blomberg2011}\cite{Blomberg2012}
\item Outline: Start with Capon's response when means for robustification are added.
\end{itemize}

Outline:
\begin{itemize}
\item Capon's resonse 
\item Choice of window functions makes little difference.
\item Steering and mainlobewidths have outer bounds.
\item Beamspace?
\item Chosen window plots - what may they tell us? Variance intensity values when using various windows.
\item Assymmetric windows?
\end{itemize}

>>>>

%%%%%%%%%%                                      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% MACROS %       
%%%%%%%%%%                                      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\newcommand\Grey[1]{{\color{Grey}#1}}
\newcommand\Red[1]{{\color{Red}#1}}
\newcommand\Blue[1]{{\color{Blue}#1}}
\newcommand\DarkBlue[1]{{\color{DarkBlue}#1}}
\newcommand\LightBlue[1]{{\color{LightBlue}#1}}
\newcommand\Brown[1]{{\color{Brown}#1}}
\newcommand\Green[1]{{\color{Green}#1}}
\newcommand\SeaGreen[1]{{\color{SeaGreen}#1}}
\newcommand\Yellow[1]{{\color{yellow}#1}}
\newcommand\Orange[1]{{\color{orange}#1}}

\newcommand\nn{\nonumber\\}

\newcommand\nmat[1]{\begin{matrix}#1\end{matrix}}
\newcommand\bmat[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand\case[1]{\begin{cases}#1\end{cases}}
\newcommand\textbox[2]{\footnotesize\text{\parbox{#1}{\centering\emph{#2}}}}

\newcommand\rand{\text{rand}}
\newcommand\randn{\text{randn}}
\newcommand\rect{\text{rect}}
\newcommand\sinc{\text{sinc}}
\newcommand\tr{\text{tr}}
\newcommand\adj{\text{adj}}

% \newcommand\max{\text{max}}
% \newcommand\min{\text{min}}

\newcommand\qqquad{\quad\qquad}
\newcommand\qqqquad{\qquad\qquad}

\renewcommand\l[1]{\left#1}
\renewcommand\r[1]{\right#1}

% {\text{\parbox{1.5cm}{\centering volume hyper- sphere}}}

%Keyword colouring:
\newcommand\kw[1]{#1}
\newcommand\parm[1]{#1}%\color{Black}#1\color{Black}}

\newcommand\of[1]{\scriptstyle(\parm{#1})\displaystyle}
\newcommand\df[1]{\scriptstyle[\parm{#1}]\displaystyle}
\newcommand\var[3]{#1_\text{#2}\of{#3}}

\newcommand\diag{\text{diag}}

% \raisebox{lift}[extend-above-baseline][extend-below-baseline]{text}
\newcommand\mt[1]{\text{\emph{#1}}} %mt = mathtext
\newcommand\mathnorm{\textstyle}
\newcommand\mathbig[1]{\displaystyle#1\mathnorm}
\newcommand\mathsmall[1]{\scriptstyle#1\mathnorm}
\newcommand\mathtiny[1]{\scriptscriptstyle#1\mathnorm}
\newcommand\sfrac[2]{\scriptstyle\raisebox{0.25pt}[0pt][0pt]{$\frac{#1}{#2}$}\mathnorm}
\newcommand\nfrac[2]{\textstyle\frac{#1}{#2}\displaystyle}

\newcommand\sumu[1]{\sum\limits^{#1}\,}
\newcommand\suml[1]{\sum\limits_{#1}\,}
\newcommand\sumb[2]{\sum\limits_{#1}^{#2}\,}

\newcommand\produ[1]{\prod\limits^{#1}\,}
\newcommand\prodl[1]{\prod\limits_{#1}\,}
\newcommand\prodb[2]{\prod\limits_{#1}^{#2}\,}

%Math macros:
\newcommand\diff[2]{\frac{\kw{d}\,\textstyle #1\scriptstyle}{\kw{d\parm{#2}}}\displaystyle}
\newcommand\ddiff[2]{\frac{\kw{d^2}\,\displaystyle #1\scriptstyle}{\kw{d\parm{#2}}^2}\displaystyle}

\renewcommand\d[1]{\scriptstyle\kw{\,d\parm{#1}}\displaystyle}

% These commands are mutually exclusive. Remember to "renew" in v2.
\newcommand\intb[4]{\int\limits_{#3}^{#4} #1 \d{#2}} % \int{exp}{var}{from}{to}
\newcommand\intl[3]{\int\limits_{#3} #1 \d{#2}} % \int{exp}{var}{for all}
\newcommand\intu[2]{\int #1 \d{#2}} % \int{exp}{var}{for all}

\newcommand\T{^{\scriptscriptstyle T}}
\renewcommand\H{^{\scriptscriptstyle H}}

\renewcommand\vec[1]{\boldsymbol{#1}}
\newcommand\mat[1]{\boldsymbol{#1}}

\renewcommand*\a{\vec a}
\renewcommand*\i{\vec i}
\renewcommand*\k{\vec k}
\newcommand*\n{\vec n}
\newcommand*\p{\vec p}
\newcommand*\s{\vec s}
\newcommand*\w{\vec w}
\newcommand*\x{\vec x}
\newcommand*\y{\vec y}

\newcommand*\A{\mat A}
\newcommand*\B{\mat B}
\newcommand*\C{\mat C}
\newcommand*\E{\mat E}
% \renewcommand*\H{\mat H}
\renewcommand*\P{\mat P}
\newcommand*\eP{\mat{\hat P}}
\newcommand*\R{\mat R}
\newcommand*\Ri{\R^{-1}}
\newcommand*\eR{\mat{\hat R}}
\newcommand*\W{\mat W}
\newcommand*\X{\mat X}
\newcommand*\Y{\mat Y}

\renewcommand*\L{\mat \Lambda}
\newcommand*\U{\mat U}
% \renewcommand*\t{\mathtiny{^T}}
% \newcommand*\h{\mathtiny{^H}}
\renewcommand*\t{^T}
\newcommand*\h{^H}

\newcommand\D{\vec\nabla} %Del: Vector differential operator - nabla
\newcommand\Dx{\vec\nabla\times}
\newcommand\Dd{\vec\nabla\cdot}

@@

\IEEEPARstart{T}{o} form images from a modern phased array sonar system the received wavefield is usually recorded, and then postprocessed by a digital beamformer. The beamformer applies delays and weights to the sensor channels, the beamformer adjusts the arrays spatial response to focus at one pixel at a time.  such that signals emanating from regions of interest add constructively, while ensuring that noise and interference from other angles do not.

@@

\begin{itemize}
\item Why beamforming?
\item Adaptive beamformers
\item Challenges in active sonar systems. Correlated noise, robustification kills the adaptive potential. Quite computationally intensive.
\item LCA is like DAS, only we test several windows and choose the one that yield the lowest beamformer output power. Ultrasound \cite{Synnevag2008}, active sonar \cite{Buskenes2011}\cite{Blomberg2011}\cite{Blomberg2012}\todo{who was first?}
\item Outline: Start with Capon's response when means for robustification are added.
\end{itemize}

Outline:
\begin{itemize}
\item Capon's resonse when applying robustification
\item Choice of window functions makes little difference.
\item Steering and mainlobewidths have outer bounds.
\item Beamspace?
\item Chosen window plots - what may they tell us? Variance intensity values when using various windows.
\item Assymmetric windows?
\end{itemize}

\begin{align}
z[n] = \sumb{m=0}{M-1} w_m[n]^*x_m[n-\Delta_m] = \w[n]\H\x_m[n-\Delta_m]
\end{align}
